%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% License:
% CC BY 3.0 (http://creativecommons.org/licenses/by/3.0/)
%
%
% Compile and build using pdfLaTeX and BibTex
% 2021: requires installation of MikTex package l3backend
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[a4paper, oneside, final, 11pt]{article} % Paper options using the scrartcl class


%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------
\usepackage[hmargin=1.65cm,vmargin=1.65cm]{geometry} % Options including margin size
\usepackage[T1]{fontenc} % Fonts
\usepackage[utf8]{inputenc} % Fonts
\usepackage{titlesec} % Allows creating custom \section's
\usepackage{helvet} % Import font
\usepackage{nopageno} % Suppress page numbers
\usepackage{fontawesome} % Icons
\usepackage{hyperref} % So URLs don't fall off the page


\expandafter\def\csname
ver@l3backend.sty\endcsname{}


\begin{document}

%----------------------------------------------------------------------------------------
%	SET UP DOCUMENT
%----------------------------------------------------------------------------------------

% Base fonts
\renewcommand*{\ttdefault}{lmvtt}

% Section and subsection headings
\titleformat{\section}{}{}{0em}{}[\titlerule]
\titleformat*{\section}{\fontfamily{phv}\bfseries\scshape\fontsize{16pt}{16pt}\selectfont} 
\titlespacing\section{0pt}{20pt plus 4pt minus 2pt}{14pt plus 2pt minus 2pt}
\titleformat*{\subsection}{\fontfamily{phv}\bfseries\scshape\fontsize{13pt}{13pt}\selectfont} 
\titlespacing\subsection{0pt}{16pt plus 4pt minus 2pt}{8pt plus 2pt minus 2pt}
\titleformat*{\subsubsection}{\fontfamily{phv}\bfseries\scshape\fontsize{11pt}{11pt}\selectfont} 
\titlespacing\subsubsection{0pt}{5pt plus 2pt minus 1pt}{4pt plus 1pt minus 1pt}

% Paragraphs
\setlength{\parindent}{0cm}


% URLs
%% Define a new 'leo' style for the package that will use a smaller font.
\makeatletter
\def\url@leostyle{%
  \@ifundefined{selectfont}{\def\UrlFont{\sf}}{\def\UrlFont{\ttfamily}}}
\makeatother
%% Now actually use the newly defined style.
\urlstyle{leo}


%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------



%----------------------------------------------------------------------------------------
% HEADER SECTION
%----------------------------------------------------------------------------------------


\makebox[1\textwidth][s]{\fontfamily{phv}\fontsize{21}{21}\bfseries\scshape{Helen Jackson, M.A.\,(Hons) Ph.D MBBS (Hons)}} % Name at the top

\bigskip

\faEnvelopeO \space helenj@ckson.io \hfill  \faMobile \space +44 7367 791625
% \faHome \space 152 Minard Road, London SE6 1NJ

\medskip

%----------------------------------------------------------------------------------------
%	PERSONAL STATEMENT
%----------------------------------------------------------------------------------------
\section{Personal Statement}
I have worked as a Senior Technology Consultant at Softwire since June 2019. I undertake client work in various roles, most commonly as delivery lead, but also as a researcher, business analyst, service designer, user researcher and software developer. \par

\smallskip

I combine a broad technical background with a keen interest in people, having studied, worked and volunteered in the healthcare technology sector for over a decade. I qualified as a medical doctor in 2017. \par

% I am passionate about technological products that address real-world user needs without over-engineering, or compromising on ingenuity or quality.
% I thrive in the space between the client and the wider technical team, where I enjoy finding evidence-based ways to balance user and business needs against product direction, technical considerations or constraints, and sustainability.
% I am organised and quick yet fastidious.
% My broad background helps me understand different types of challenges and different types of people.\par

\medskip

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}

\subsubsection*{MBBS (Hons), Graduate-entry Medicine, King's College London \hfill 2017}  
\normalfont{
Completed placements in all standard training disciplines including medicine, surgery, general practice, psychiatry and various specialties \\
Assessed in Advanced Life Support \\
Authored or co-authored two published peer-reviewed original research articles, two published peer-reviewed conference abstracts, six conference research posters and eight conference oral presentations
}

\bigskip

\subsubsection*{Ph.D, University of Cambridge \hfill 2011}  
\normalfont{
	``The role of temporal information in the perception of complex signals", Prof.\,Brian C.\,J.\,Moore  \\
	\textit{https://github.com/DeckOfPandas/phd}  \\
	First author of three published peer-reviewed original research articles \\
	Co-authored two published peer-reviewed conference abstracts and two conference research posters
}

\bigskip

\subsubsection*{M.A.\,(Hons), Natural Sciences, University of Cambridge \hfill 2007}  
\normalfont{
	Classification: II(i)  \\
	Part II course: Experimental Psychology \\
	Part I courses: Anatomy, Biochemistry, Medical Sociology and Statistics, Neurobiology, Pathology, Pharmacology, Physiology, Reproductive Biology
}

\medskip

%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------
\section{Experience}

\subsubsection*{Senior Technology Consultant, Softwire \hfill June 2019--present}  
\normalfont

\bfseries National Physical Laboratory, Python developer \hfill November 2020 to January 2021
\normalfont
\begin{itemize}
	\item Joined a technical lead to build a comprehensive analysis suite using Python, numerical, scientific and plotting Python packages, SQLite and SQLAlchemy, for Lidar measurements of atmospheric pollutants
	\item Translated complicated business requirements and MATLAB scripts into a fully featured, extensible and maintainable Python application, with automated testing and building via a Continuous Integration pipeline
	\item Manipulated data, implemented complex mathematical calculations, and built a GUI 
\end{itemize} 

\smallskip

\bfseries Cabinet Office, Delivery Lead / Service Designer \hfill May to November 2020
\normalfont
\begin{itemize}
	\item Led Discovery and Alpha phases of research into absent voting processes, involving quantitative and qualitative research, interviewing electoral administrators and designing potential technical service options
	\item Acted as the primary client contact point, co-ordinating all stakeholders across central and local government
	\item Led a cross-organisational team through a GDS Assessment of the proposed new service, passing at the first attempt
\end{itemize} 

\smallskip

\bfseries Public Health England, Business Analyst \hfill March to April 2020
\normalfont
\begin{itemize}
	\item Co-led a small team in a Discovery into data collection, visualation and governance activities carried out by different departments, to inform the future design of a consolidated and modernised health intelligence system
	\item Designed and conducted detailed interviews to establish the technical landscape for potential improvements
	\item Produced a detailed structured document describing key data-related activities to inform future prototyping
\end{itemize} 

\smallskip

\bfseries Public Health England, Delivery Lead \hfill November 2019 to February 2020
\normalfont
\begin{itemize}
	\item Led a team in a technical Discovery investigating options for upgrading PHE's Cancer Analysis System, a complicated set of databases containing disparate datasets used by analysts to produce cancer epidemiology metrics and guide research
	\item Acted as the primary client contact point, co-ordinating all project stakehokders and activities
	\item Carried out technical and user research
	\item Produced a detailed written report into upgrade options, including migration plans, indicative cost estimates, and a roadmap for the Alpha phase of the research
\end{itemize} 

\smallskip

\bfseries Tate Britain, Business Analyst / User Researcher \hfill September to October 2019
\normalfont
\begin{itemize}
	\item Interviewed a wide cross-section of Tate staff, identifying and analysing all relevant workflows
	\item Produced an architectural plan and indicative time and cost estimates for the replacement of the Tate website's Content Management System, including integrations with the wider Tate IT estate
	\item Shortlisted potential replacement approaches, outlining both the technical and user-facing benefits of each option
	\item Advised on the simplification of business processes, and opportunities for legacy system replacement or consolidation. \\
\end{itemize}

\smallskip 

\subsubsection*{Freelance health, research and technology consultant \hfill 2014--2019}  
\normalfont
\begin{itemize}
	\item Researched and prototyped Open Spirometer, an Android app for Open Health Care UK, to measure lung function using just a device's microphone\\
	\textit{http://openspirometer.org}
	\item Co-ordinated a team of doctors and developers to build Take Your Meds, a prizewinning telephone-based medication reminder system using Python and Django and the Twilio service\\
	\textit{http://helenjackson.co.uk/take-your-meds} (temporary demonstration site)
	\item Co-ordinated a team of doctors and developers to install and maintain a fully featured online research data collection platform on AWS for the Welsh Digital Data Collection Platform, used for clinical studies across Wales\\
	\textit{http://wddcp.ac.uk}
	\item Designed and built a static website using Jekyll for Too Much of a Person, a community movement and exhibition; set up continuous integration with testing and deployment in a way that allowed non-technical people to update content and add media to a portfolio without further technical input\\
	\textit{http://toomuchofaperson.com}
	\item Researched and wrote up the health economics business case for a technology hardware startup
	\item Took principal role to scope, design, brand and deliver a corporate-level hackathon-as-a-service for the community development arm of a big pharma company\\
	\textit{http://nhsideaslab.com}
\end{itemize}

\smallskip 

\subsubsection*{Co-Founder \& Technology Lead, JSAMR (volunteer) \hfill 2016--present} 
\normalfont
\begin{itemize}
	\item Founded JSAMR, the Journal of the Student Association for Medical Research, an online open access and open source academic journal for medical student research from scratch \\
	\textit{http://nsamr.ac.uk/journal}
	\item Installed and customised Open Journal Systems (OJS) software, written in PHP on top of a PostgreSQL database, to build a fully featured online submission, review and publication system
	\item Completely redesigned public OJS frontend to allow modern, usable design, using HTML, CSS and preprocessors, and JavaScript
\end{itemize}

\smallskip 
				
\subsubsection*{Technology Lead \& Trustee, NSAMR (volunteer) \hfill 2016--2018}  
\normalfont
\begin{itemize}
	\item Supported all technological aspects of the research charity NSAMR, National Student Association for Medical Research, including setting up version control, monitoring and recovery systems for the main website and sub-team activities\\
	\textit{http://nsamr.ac.uk/}
\end{itemize}

\smallskip 

\subsubsection*{NHS Hack Day core team member (volunteer) \hfill 2014--2018}  
\normalfont
\begin{itemize}
	\item Contributed to the organisation of sixteen health and care technology hackathons with the tagline ``Making NHS IT Less Bad", four as lead or sole organiser\\
	\textit{http://nhshackday.com/}
\end{itemize}

\smallskip 
				
\subsubsection*{Research consultant, Meridian Audio Ltd then MQA Ltd \hfill 2014--2016}  
\normalfont
\begin{itemize}
	\item Led the planning, delivery, analysis and writeups of psychoacoustic experiments investigating high-resolution audio
	\item Designed and investigated digital filters using MATLAB, processing signals and building a frontend application to run the behavioural testing paradigms
	\item First author of publication winning ``best peer-reviewed paper" at the Audio Engineering Society 137$^{th}$ Annual Conference
\end{itemize}

\smallskip 
				
\subsubsection*{Research consultant, Eriksholm Research Centre, Oticon, Denmark \hfill 2011--2012}  
\normalfont
\begin{itemize}
	\item Built a web application using Flash and AS3 to deliver an online battery of hearing tests for measuring sensitivity to temporal fine structure, used as part of the FAS-IT study which was undertaken by $>$1500 participants
\end{itemize}

\smallskip 

\subsubsection*{Supervisor of undergraduate students, University of Cambridge \hfill 2007--2012} 
\normalfont
\begin{itemize}
	\item Planned and delivered tutorials to small groups of undergraduate students covering Part II and Part IB courses in hearing, neurobiology and statistics
	\item Queens' College graduate Teaching Fellow for Part IB Experimental Psychology course, 2009--2010
\end{itemize}

\medskip


%----------------------------------------------------------------------------------------
%	FURTHER INFORMATION
%----------------------------------------------------------------------------------------
% \section{Further information}
%\begin{itemize}
%	\item Interests: violin, chamber music, food and drink, knitting
% \end{itemize}


\newpage

%----------------------------------------------------------------------------------------
%	APPENDIX
%----------------------------------------------------------------------------------------
\section{Appendix}

\subsection*{Peer-reviewed original research}

Byrne M, Stainer B, Symington M, Leighton J, \textbf{Jackson HM}, Singhal N, Shiel-Rankin S, Mayes J, Mogg J, Bonham T, Smit A, Deutsch E, Thompson E, Wilson C. School level education to increase organ donation and awareness of issues in transplantation in the UK. \textit{Transplant International}. (in press).

\bigskip

Byrne M, Symington M, Stainer B, Leighton J, \textbf{Jackson HM}, Singhal N, Shiel-Rankin S, Mayes J, Mogg J, Bonham T, Smit A, Deutsch B, Wilson C. School level education to increase organ donation and the effect of deprivation. \textit{International Journal of Surgery}. 2018; 55:s5. \url{https://doi.org/10.1016/j.ijsu.2018.05.695}. \textbf{Winner of ASGBI/ASiT Short Paper Prize}. [published conference abstract].

\bigskip

Byrne M, \textbf{Jackson HM}, Sinha A, Tong A, Grafton-Clarke C, Rees S, Mathur A, Cross B, Christopher E, Isaacs L, Banh S, Sheng Z, Lundin R. The National Student Association of Medical Research (NSAMR) Publication Pathway. \textit{International Journal of Surgery}. 2017; 47:s55. \url{https://doi.org/10.1016/j.ijsu.2017.08.287}. [published conference abstract].

\bigskip

\textbf{Jackson HM}, Capp MD, Stuart JR. The audibility of typical digital audio filters in a high-fidelity playback system. \textit{Audio Engineering Society 137$^{th}$ International Conference}. 2014; 1-12. \url{http://www.aes.org/e-lib/browse.cfm?elib=17497}. Accessed October 9, 2014. \textbf{Prize for best peer-reviewed paper}.

\bigskip

\textbf{Jackson HM}, Moore BCJ. The role of excitation-pattern, temporal-fine-structure and envelope cues in the discrimination of complex tones. \textit{Journal of the Acoustical Society of America}. 2014; 135:1356-1370. \url{https://doi.org/10.1121/1.4864306}.


\bigskip
\textbf{Jackson HM}, Moore BCJ. The dominant region for the pitch of complex tones with low fundamental frequencies. \textit{Journal of the Acoustical Society of America}. 2013; 134:1193-1204. \url{https://doi.org/10.1121/1.4812754}.

\bigskip

\textbf{Jackson HM}, Moore BCJ. Contribution of temporal fine structure information and fundamental frequency separation to intelligibility in a competing-speaker paradigm. \textit{Journal of the Acoustical Society of America}. 2013; 133:2421-2430. \url{https://doi.org/10.1121/1.4792153}.

\bigskip

\textbf{Jackson HM}, Moore BCJ. Evaluation of the relative importance of temporal-fine-structure and excitation-pattern cues in the discrimination of complex tones with high harmonics. \textit{International Journal of Audiology}. 2011; 50(10):717-780. \url{https://doi.org/10.3109/14992027.2011.588967}. [published conference abstract].

\bigskip

\textbf{Jackson HM}, Moore BCJ. Factors influencing sensitivity to temporal fine structure in normal-hearing listeners. \textit{International Journal of Audiology}. 2010; 49(9):672-722. \url{https://doi.org/10.3109/14992027.2010.490242}. [published conference abstract].

\bigskip



\subsection*{Poster presentations, abstracts, oral presentations and conference lectures}

Rapid-fire oral and poster presentation: Byrne M, Rees S, \textbf{Jackson HM}, Harvey A, Tong G, Brezovjakova H. Journey of a Journal: the use of a student-run peer reviewed journal as a learning tool. \textit{UK Clinical Teaching Fellows Forum and Academy of Medical Educators, Frimley Park Hospital, UK}. 2019.

\bigskip

Rapid-fire oral poster presentation: Dalton T, \textbf{Jackson HM}. Making Sense of Psychopathology: The importance of undergraduate teaching on the function and phenomenology of symptoms. \textit{Royal College of Psychiatrists International Congress, Birmingham, UK}. 2018.

\bigskip

Oral presentation and poster: Dalton T, \textbf{Jackson HM}. Making Sense of Psychopathology: The importance of undergraduate teaching on the function and phenomenology of behavioural symptoms. \textit{National Foundation Doctors Research Presentation Day, Bristol, UK}. 2018. \textbf{Highly commended (Education category)}.

\bigskip

Oral presentation and poster: Byrne M, Symington M, Stainer B, Leighton J, \textbf{Jackson HM}, Singhal N, Shiel-Rankin S, Mayes J, Mogg J, Bonham T, Smit A, Deutsch B, Wilson C. School level education to increase organ donation and the effect of deprivation. \textit{National Foundation Doctors Research Presentation Day, Bristol, UK}. 2018.

\bigskip

Oral presentation and conference short paper: Byrne M, Symington M, Stainer B, Leighton J, \textbf{Jackson HM}, Singhal N, Shiel-Rankin S, Mayes J, Mogg J, Bonham T, Smit A, Deutsch B, Wilson C. School level education to increase organ donation and the effect of deprivation. \textit{Association of Surgeons in Training 2018, Edinburgh, UK}. 2018. \textbf{Winner of ASGBI/ASiT Short Paper Prize}. Published: \textit{International Journal of Surgery}. 2018; 55:s5. \url{https://doi.org/10.1016/j.ijsu.2018.05.695}.

\bigskip

Poster: Dalton T and \textbf{Jackson HM}. Medical students and phenomenology: presenting simple, coherent schemas of psychopathological processes. \textit{Annual RCPsych Medical Education Conference, Belfast, UK}. 2017.

\bigskip

Oral presentation: \textbf{Jackson HM}. Sense of presence experiences and the neuropsychiatry of Parkinson's disease. \textit{Royal College of Psychiatrists International Congress, Edinburgh, UK. 2017}.

\bigskip

Poster and published abstract: Byrne M, \textbf{Jackson HM}, Sinha A, Tong A, Grafton-Clarke C, Rees S, Mathur A, Cross B, Christopher E, Isaacs L, Banh S, Sheng Z, Lundin R. The National Student Association of Medical Research (NSAMR) Publication Pathway. \textit{Association of Surgeons in Training 2017, Bournemouth, UK}. 2017. Published: \textit{International Journal of Surgery}. 2017; 47:s55. \url{https://doi.org/10.1016/j.ijsu.2017.08.287}.

\bigskip

Poster: \textbf{Jackson HM}. Sense of presence experiences in Parkinson's disease. \textit{Royal College of Psychiatrists International Congress, London, UK}. 2016.

\bigskip

Conference lecture and paper: \textbf{Jackson HM}, Capp MD, Stuart JR. The audibility of typical digital audio filters in a high-fidelity playback system. \textit{Audio Engineering Society 137$^{th}$ International Conference, San Francisco, United States}. 2014. \textbf{Winner of prize for best peer-reviewed paper}.

\bigskip

Conference lecture: \textbf{Jackson HM}. Psychoacoustics over the internet: temporal fine structure as a screening tool? \textit{International Meeting on Internet \& Audiology, Link{\"o}ping, Sweden}. 2014.

\bigskip

Conference workshop: \textbf{Jackson HM}. How to run a Hack Day. \textit{SpotOn: Science Policy, Outreach and Tools Online}, London, UK. 2013.

\bigskip

Conference lecture: \textbf{Jackson HM}, Wong WK. NHS Hack Day and Innovation within the NHS. \textit{Health Services Research Network Symposium}, Manchester, UK. 2013.

\bigskip

Poster and published abstract: \textbf{Waller HM}, Moore BCJ. Evaluation of the relative importance of temporal-fine-structure and excitation-pattern cues in the discrimination of complex tones with high harmonics. \textit{British Society of Audiology Annual Conference, Manchester, UK. 2010}. Published: Abstracts of the British Society of Audiology Annual Conference September 8--10, 2010, School of Psychological Sciences, University of Manchester, UK. \textit{International Journal of Audiology}. 2011; 50(10):717-780. \url{https://doi.org/10.3109/14992027.2011.588967}.

\bigskip

Poster and published abstract: \textbf{Waller HM}, Moore BCJ. Factors influencing sensitivity to temporal fine structure in normal-hearing listeners. \textit{British Society of Audiology Short Papers meeting, Southampton, UK}. 2009. Published: Abstracts of the British Society of Audiology Short Papers Meeting on Experimental Studies of Hearing and Deafness, September 17--18, 2009, Institute of Sound and Vibration Research, University of Southampton, UK. \textit{International Journal of Audiology}. 2010; 49(9):672-722. \\\url{https://doi.org/10.3109/14992027.2010.490242}.

\end{document}
